An equivalence of compositional frameworks

### 2019-05-28 EquivCompFrameworks_20180911kc.tex
tiny notation

\begin{proof}
Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $d\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $\iota\colon(Fk)(d)\to d'$, see \cref{eq:FCsp2morph}.

>>>>

\begin{proof}
Recall that the double category of decorated cospans $\dcsp{F}$ has objects and vertical 1-morphisms those of $\A$, horizontal 1-cells $a\tickar b$ are cospans $\cspn{a}{c}{b}{}{}$ in $\A$ along with $x\in F(c)$, and 2-morphisms are cospan maps $k\colon c\to c'$ together with a morphism $(Fk)(x)\to x'$, see \cref{eq:FCsp2morph}.
